---
title: "Instruction for using bicorr codes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Adjusting codes
### Read  in Data
1. Give the name of the data file to the variable named option.(option = "FEMALE.txt" in sample codes)
2. Specify the number of rows contained in the data file.(apoE<-read.table(option,nrows = 23568) in sample codes,change 23568 to the number of rows in your data file)
### Data cleaning
The data matrix after data cleaning should be a matrix whose column names are gene names and each row represents for observations of one individual over all different genes.
```{r cars}
summary(cars)
```
### Organize the output
1. You can change the desired p-value for your needs.(result <- result[result$p<0.1,] in sample codes, you may change 0.1 to another value) 
### Save the result
1. Change the name of your output.(save(result,file = "2_apoE_FEMALE_bicorr.Rdata") in sample codes)


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
